### 2020-08-04 doc/manuscript/Dow_manuscript.Rmd
transferred content from previous Word doc

**Title:**

@@

@@

>>>>

**Title:** Effect of spring temperatures on tree growth phenology in a temperate deciduous forest

@@

**With climate warming, we can expect earlier springs in temperate forests.** 
These are likely to affect tree growth, woody productivity, and ecosystem C cycling.
However, we know little about the growth phenology of temperate deciduous species (see D’Orangeville et al., in revision for more info/ citations)—let alone how these are affected by an early spring.

Here, we ...
- use 10 years of biweekly dendro band measurements for # species to characterize seasonal growth phenology

- combine these records with 110 years of tree-ring data for 12 species to examine how spring temperatures impact annual tree growth

- examine the effects of an extremely early spring (2020) seasonal growth phenology and annual growth

#### Study site and data
SCBI ForestGEO plot

10 years biweekly dendrometer measurements

leaf phenology data?

- leaf phenology data from NEON and/or satellite-based (leaf phenology network: https://www.usanpn.org/news/spring) ?

- NDVI or PRI? https://onlinelibrary.wiley.com/doi/10.1111/gcb.15112 (from Ian)

- From Ian:  I noticed how the growth patterns observed by remote sensing pretty much mirror what Sean was finding with his dendro R package (btw is that functional on CRAN yet?) for both SERC and SCBI dendroband data.

perhaps bring in cores?

#### Analysis

@@

*Content to incorporate:
N. American strategies have conservative strategies when it comes to phenology, as historically they’ve been subject to more spring frosts. Thus, climate change is having less impact [@zohner_late-spring_2020]*
